\documentclass[12pt]{article}
\title{First Bit}

\begin{document}

\section{Traditionally...}

There was just html css and javascript to begin with, but this mean we had to
accomadate different browsers.

Jquery came along and allowed developers to interact with the DOM. Jquery had an
easy developed UI.

JS files started getting very large making it hard to organize JS files.

Started to shift to more focus on JavaScript over the html and css.

Creation of single page applications allowed browsers to load the webpage once.

Angular JS came out in 2010 from Google.

Code had better containers with the MVC architecture.

2013: React comes out, released by Facebook.

Angular JS devided to rewrite to Angular.

React is the most popular front-end tool.

\section{React Concepts}
\begin{enumerate}
    \item Imperative, previous frameworks manupulating the DOM. Directly change
        individual parts of your app.

    \item React goes for Declarative approach. DOM manipulation is a bottleneck,
        must repaint, then refloat the page. Declare what the app looks like and
        react will create the object.

    \item One javascript object is used to describe how the app should look.

    \item React means based on whatever the state is, react will react to it.
\end{enumerate}

\begin{itemize}
    \item React decided to use components to create an app.
    \item Small components are added together to create a full app.
    \item Similar to building with lego blocks
    \item React bootstrap or blueprint components are used for simple templating
        when creating a new app.
    \item Components are functions that return HTML that receive props.
\end{itemize}

\section{Why React}
\begin{itemize}
    \item Create a simple state to create components.
    \item React is a function that takes the state and the components and creates
        a virtual DOM.
    \item Unidirectional data flow
    \item UI, the rest is up to you
    \item Can use React in mobile, desktop, vr, terminal, really anywhere
\end{itemize}

\section{The Job of a React Developer}
\begin{enumerate}
    \item Decide on the Components
    \item Decide the State and where it lives
    \item What changes when state changes
\end{enumerate}



\end{document}

